---
title: "Develop Data Product - Predict Car Display"
author: "Yvonne"
date: "May 4, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Develop Data Product - Week 4 Assignment

As part of the requirement of the Module 9 (Develop Data Product), it's required to develop a Shiny web application and to present a pitch.

- The shiny web application has been generated using RStudio(https://www.rstudio.com) and Shiny.io(https://www.shinyapps.io/).

- A  presentation was also created to describe what is being done in the Shiny web application. The presentation was generated using RStudio(https://www.rstudio.com) and Slidify(http://slidify.org) framework.

## Shiny Web Appliction - Predicting Display using Horsepower

The Shiny web application was developed to predict the Display of a car by using its horsepower. The app is shared here: https://yvonneleong.shinyapps.io/Week4_Project/. 


- In the application, a prediction model is generated, based on a car dataset (mtcars) which consists of parameters like Horsepower, Display, Miles Per Gallon, etc. 
- Then, user can select the horsepower in order to predict the Display of the car.  
- The 'point' showing the predicted Display will be shown on the plot and the figure for the Display will be shown at below the plot.

The application and the current presentation source codes can be found here https://github.com/yvonnellh/09-DevelopDataProduct.


## Datasets Used in Prediction Model

```{r, echo=TRUE}
summary(mtcars)
```

## Prediction Plot for Display Vs Horsepower

```{r, echo=TRUE}
model1 <- lm(disp ~ hp, data = mtcars)
plot(mtcars$hp, mtcars$disp, xlab = "Horsepower",
         ylab = "Display", bty = "n", pch = 16,
         xlim = c(0, 350), ylim = c(0, 600))
abline(model1, col = "red", lwd = 2)
```

